### 2019-02-25 manuscript/results.tex
- suggestions in Results - small modification to supp table legend in Results - check author info note!

We found that when considered alone, ploidy and breeding system each showed significant associations with net diversification differences. %B: check and deleteme: I think this should have "states" added, so "...ploidy and breeding system states showed..."
When considered together, however, the effect of breeding system dominated the effect of ploidy, although hidden factors played an important role as well. %B: same here.

@@

When considering breeding system alone, we found a larger net diversification rate for SI than for SC species, in agreement with \citet{goldberg_2010} (I/C model, \cref{figure:netdivall}C).
When a hidden state is included (I/C+A/B model), the large net diversification difference persists for one of the hidden states but is removed for the other (\cref{figure:netdivall}D).
Thus, differences in net diversification are best explained by both breeding system and an unknown factor.
% The transition rate from SI to SC is $q_{IC}=0.3$ for both the I/C and the I/C+A/B models.
The statistical model comparison shows very strong support for including the hidden state (\cref{table:bayesfactors}).

@@

We considered models both with or without diploidization in order to explore the effects of this process on the estimates of state-dependent diversification.
For the two models that only include diploid and polyploid states (D/P and D/P+A/B), the net diversification rate of polyploid lineages is likely negative when diploidization (parameter $\delta$) is excluded but positive when $\delta$ is included (\cref{figure:netdivall}A versus \cref{figure:netdivnodip}A).
For the two models that also included breeding system (ID/CD/CP and ID/CD/CP+A/B), the main effect of including diploidization is increasing the uncertainty of the estimate of polyploid net diversification rate (\cref{figure:netdivall}EF versus \cref{figure:netdivnodip}CD).
For all models, there is greater uncertainty in the estimate of diploidization rate than polyploidization rate, as judged by the width of the credibility intervals (see supplementary information figures). % todo: precise figure refs here
% E: Rosana, would this also be a good place to say something about what we learned regarding the meaningfulness of diploidization in these data?

@@

Polyploidization rates from self-compatible diploid $\rho_{CD}$ and from self-incompatible diploid $\rho_{ID}$ are not significantly different (see supplementary information figures).
However, the distribution of $\rho_{ID}$ seems to always consider faster values compare to the distribution of $\rho_{CD}$.
This result is highlighted in ancestral reconstructions of the $ID/CD/CP$ model where transitions from ID to CP are more probable than transitions from CD to CP. % Emma here we put the figure?

\begin{supptable}
    \begin{center}
    \begin{tabular}{lcccccc}
                       & D/P   & D/P+A/B      & I/C    & I/C+A/B      & ID/CD/CP & ID/CD/CP+A/B \\ \midrule
        %                                                                                      
        $r_D$          & 0.382 & 0.698, 0.100 & ---    & ---          & ---      & ---          \\
        $r_P$          & 0.109 & 0.587, 0.182 & ---    & ---          & ---      & ---          \\
        $r_I$          & ---   & ---          & 0.550  & 0.386, 0.877 & ---      & ---          \\
        $r_C$          & ---   & ---          &-0.001  &-0.059, 0.606 & ---      & ---          \\
        $r_{ID}$       & ---   & ---          & ---    & ---          & 0.449    & 0.318, 0.789 \\
        $r_{CD}$       & ---   & ---          & ---    & ---          & 0.050    &-0.248, 0.494 \\
        $r_{CP}$       & ---   & ---          & ---    & ---          &-0.027    & 0.110, 0.634 \\
        %                                                                                      
        $\rho$         & 0.033 & 0.026        & ---    & ---          & ---      & ---          \\
        $\rho_I$       & ---   & ---          & ---    & ---          & 0.063    & 0.047        \\
        $\rho_C$       & ---   & ---          & ---    & ---          & 0.024    & 0.011        \\
        $\delta$       & 0.050 & 0.162        & ---    & ---          & 0.022    & 0.107        \\
        $q_{IC}$       & ---   & ---          & 0.364  &              & 0.194    & 0.164        
    \end{tabular}

    \vspace{12pt}
    \begin{tabular}{lcccc}
                       & D/P   & D/P+A/B      & ID/CD/CP & ID/CD/CP+A/B \\ \midrule
        %                                                              
        $r_D$          & 0.260 & 0.193, 0.658 & ---      & ---          \\
        $r_P$          &-0.056 & 0.030, 0.187 & ---      & ---          \\
        $r_I$          & ---   & ---          & ---      & ---          \\
        $r_C$          & ---   & ---          & ---      & ---          \\
        $r_{ID}$       & ---   & ---          & 0.455    & 0.309, 0.797 \\
        $r_{CD}$       & ---   & ---          & 0.065    &-0.006, 0.587 \\
        $r_{CP}$       & ---   & ---          &-0.088    &-0.074, 0.403 \\
        %                                                              
        $\rho$         & 0.047 & 0.047        & ---      & ---          \\
        $\rho_I$       & ---   & ---          & 0.067    & 0.053        \\
        $\rho_C$       & ---   & ---          & 0.033    & 0.032        \\
        $q_{IC}$       & ---   & ---          & 0.198    & 0.145        
    \end{tabular}
    \end{center}
    \caption{
        Median rate estimates for all models.
        Units are per million years.
        Two comma-separated numbers refer to the $A$ and $B$ hidden states, and --- means the parameter was not present in the model.
        The upper section is for models with diploidization, and the lower section is for models without.
        The supplemental figures show the corresponding distributions of parameter estimates.
    }
    \label{table:estimates}
\end{supptable}

@@

\begin{suppfigure}
\includegraphics[width=\textwidth]{bisseDPposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P polyploidy model} % XXX
\label{suppfigure:DP}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{bisseDPnodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P no $\delta$ polyploidy model} % XXX
\label{suppfigure:DPnodip}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{hisseDPposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P-A/B polyploidy model} % XXX
% fixme: offset plotting error in "relative extinction" panel
\label{suppfigure:DPAB}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{hisseDPnodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P no $\delta$-A/B polyploidy model} % XXX
\label{suppfigure:DPnodipAB}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{bisseSIposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the I/C breeding system model} % XXX
\label{suppfigure:IC}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{hisseSInoretposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the I/C-A/B breeding system model} % XXX
\label{suppfigure:ICAB}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{musseDPSIposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCP}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{musseDPSInodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP no $\delta$ polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCPnodip}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{muhisseDPSIposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP-A/B polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCPAB}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{muhisseDPSInodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP no $\delta$- A/B polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCPnodipAB}
\end{suppfigure}

>>>>

We found that when considered alone, ploidy and breeding system each showed significant associations with net diversification differences. 
When considered together, however, the effect of breeding system dominated the effect of ploidy, although hidden factors played an important role as well.

@@

When considering breeding system alone (I/C model, \cref{figure:netdivall}C), we found a larger net diversification rate for SI than for SC species, in agreement with \citet{goldberg_2010}. %B: moved \cref{} earlier; avoids seeming related to \citep{}
When a hidden state is included (I/C+A/B model), the large net diversification difference persists for one of the hidden states but is removed for the other (\cref{figure:netdivall}D).
Thus, differences in net diversification are best explained by both breeding system and an unknown factor.
% The transition rate from SI to SC is $q_{IC}=0.3$ for both the I/C and the I/C+A/B models.
The statistical model comparison shows very strong support for including the hidden state (\cref{table:bayesfactors}).

@@

We considered models both with or without diploidization in order to explore the effects of this process on the estimates of state-dependent diversification.
For the two models that only include diploid and polyploid states (D/P and D/P+A/B), the net diversification rate of polyploid lineages is likely negative when diploidization (parameter $\delta$) is excluded but positive when $\delta$ is included (\cref{figure:netdivall}A versus \cref{figure:netdivnodip}A).
For the two models that also included breeding system (ID/CD/CP and ID/CD/CP+A/B), the main effect of including diploidization is increasing the uncertainty of the estimate of polyploid net diversification rate (\cref{figure:netdivall}EF versus \cref{figure:netdivnodip}CD).
For all models, there is greater uncertainty in the estimate of diploidization rate than polyploidization rate, as judged by the width of the credibility intervals (see supplementary information figures). % todo: precise figure refs here
% E: Rosana, would this also be a good place to say something about what we learned regarding the meaningfulness of diploidization in these data?
%B: maybe meaning of the data could go to a dedicated Discussion subsection? The idea would be to reconcile variation in $\delta$ across (the best-fitting) models considered here, and how the implied values do (or do not) agree with chromosome number changes and WGD inference from tree reconciliation and Ks approaches. (I can help here, if needed.)

@@

Polyploidization rates from self-compatible diploid $\rho_{CD}$ and from self-incompatible diploid $\rho_{ID}$ are not significantly different (see supplementary information figures).
However, the distribution of $\rho_{ID}$ seems to always consider faster values compare to the distribution of $\rho_{CD}$.
This result is highlighted in ancestral reconstructions of the $ID/CD/CP$ model where transitions from ID to CP are more probable than transitions from CD to CP. % Emma here we put the figure?
%B: I am not sure I understand the "However, " sentence. TODO.

\begin{supptable}
    \begin{center}

    \begin{tabular}{lcccc}
                       & D/P   & D/P+A/B      & ID/CD/CP & ID/CD/CP+A/B \\ \midrule
        %                                                              
        $r_D$          & 0.260 & 0.193, 0.658 & ---      & ---          \\
        $r_P$          &-0.056 & 0.030, 0.187 & ---      & ---          \\
        $r_I$          & ---   & ---          & ---      & ---          \\
        $r_C$          & ---   & ---          & ---      & ---          \\
        $r_{ID}$       & ---   & ---          & 0.455    & 0.309, 0.797 \\
        $r_{CD}$       & ---   & ---          & 0.065    &-0.006, 0.587 \\
        $r_{CP}$       & ---   & ---          &-0.088    &-0.074, 0.403 \\
        %                                                              
        $\rho$         & 0.047 & 0.047        & ---      & ---          \\
        $\rho_I$       & ---   & ---          & 0.067    & 0.053        \\
        $\rho_C$       & ---   & ---          & 0.033    & 0.032        \\
        $q_{IC}$       & ---   & ---          & 0.198    & 0.145        
    \end{tabular}

            \vspace{12pt}

    \begin{tabular}{lcccccc}
                       & D/P   & D/P+A/B      & I/C    & I/C+A/B      & ID/CD/CP & ID/CD/CP+A/B \\ \midrule
        %                                                                                      
        $r_D$          & 0.382 & 0.698, 0.100 & ---    & ---          & ---      & ---          \\
        $r_P$          & 0.109 & 0.587, 0.182 & ---    & ---          & ---      & ---          \\
        $r_I$          & ---   & ---          & 0.550  & 0.386, 0.877 & ---      & ---          \\
        $r_C$          & ---   & ---          &-0.001  &-0.059, 0.606 & ---      & ---          \\
        $r_{ID}$       & ---   & ---          & ---    & ---          & 0.449    & 0.318, 0.789 \\
        $r_{CD}$       & ---   & ---          & ---    & ---          & 0.050    &-0.248, 0.494 \\
        $r_{CP}$       & ---   & ---          & ---    & ---          &-0.027    & 0.110, 0.634 \\
        %                                                                                      
        $\rho$         & 0.033 & 0.026        & ---    & ---          & ---      & ---          \\
        $\rho_I$       & ---   & ---          & ---    & ---          & 0.063    & 0.047        \\
        $\rho_C$       & ---   & ---          & ---    & ---          & 0.024    & 0.011        \\
        $\delta$       & 0.050 & 0.162        & ---    & ---          & 0.022    & 0.107        \\
        $q_{IC}$       & ---   & ---          & 0.364  &              & 0.194    & 0.164        
    \end{tabular}

    \end{center}
    \caption{
        Median rate estimates for all fitted models. %B: "...all fitted/considered/evaluated models."
        Units are per million years.
        Two comma-separated numbers refer to the $A$ and $B$ hidden states, and --- means the parameter was not present in the model.
    %B: perhaps include this in the table so lazies don't have to go seeking subscripts?
    Net diversification rates ($r$) are subscripted with trait state initials (Diploid, Polyploid, Incompatible, Compatible). Transition rates are $\rho$ (polyploidization), subscripted with background breeding system state; $\delta$ (diploidization); and  $q_{IC}$ (loss of self-incompatibility).
    The upper section is for models without diploidization, and the lower section is for models with diploidization.
    The supplemental figures show the corresponding distributions of parameter estimates.
    }
    \label{table:estimates}
\end{supptable}
%B: The I/C and I/C+A/B columns should be in the top panel, no (they don't have rho)? I'll do this in a separate doc first. %FIXME

@@

\begin{suppfigure}
\includegraphics[width=\textwidth]{bisseDPposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P, polyploidy model} % XXX
\label{suppfigure:DP}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{bisseDPnodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P no $\delta$, polyploidy model} % XXX
\label{suppfigure:DPnodip}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{hisseDPposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P+A/B, polyploidy model} % XXX
% fixme: offset plotting error in "relative extinction" panel
\label{suppfigure:DPAB}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{hisseDPnodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P no $\delta$+A/B, polyploidy model} % XXX
\label{suppfigure:DPnodipAB}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{bisseSIposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the I/C, breeding system model} % XXX
\label{suppfigure:IC}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{hisseSInoretposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the I/C+A/B, breeding system model} % XXX
\label{suppfigure:ICAB}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{musseDPSIposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP, polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCP}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{musseDPSInodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP no $\delta$, polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCPnodip}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{muhisseDPSIposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP+A/B, polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCPAB}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{muhisseDPSInodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP no $\delta$+A/B polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCPnodipAB}
\end{suppfigure}
